Analyses

### 2021-11-19 src/analysis/analyses.Rmd
add new analysis

kbl(cfa1, booktabs =T, caption = "Confirmatory Factor Analysis") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "10cm") %>%
  column_spec(2, width = "3cm") 
```

>>>>

kbl(m_cfa, booktabs =T, caption = "Confirmatory Factor Analysis - Fit Statistics") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "4cm")  %>%
  column_spec(2, width = "4cm") %>%
  column_spec(2, width = "4cm")

kbl(cfa1, booktabs =T, caption = "Confirmatory Factor Analysis") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "10cm") %>%
  column_spec(2, width = "3cm")

cfa2
```
